InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-29 paper.tex

The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI. In the training stage the detector tryed to differentiate between human and AI text while a paraphraser trained to make the text more human.
The Ai-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.

>>>>

The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI. In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
